---
title: "Stat 435 Project"
author: "Brian Bruxvoort"
date: '2023-10-26'
output:
  word_document: default
  pdf_document: default
---


# Part 1
Perform a Wald test for a βjr for some r = 1, · · · , p. Why may this test not be of interest?
```{r}
wheat <- read.csv("wheat.csv")
```

```{r}
library(package = nnet)
mod.fit.nom.density <- multinom(formula = type ~ class + density + hardness + size + weight + moisture, data = wheat)
summary(mod.fit.nom.density)
```

We might not be interested in the Wald results because they are not as accurate as some of the other tests.

# Part 2
How can we perform a LRT for an explanatory variable?
```{r, message=FALSE, warning=FALSE}
library(package = car)
Anova(mod = mod.fit.nom.density, test = "LR")
```

# Part 3
How can we estimate in R the probability of healthy for the first observation?
```{r}
new_data <- wheat[1,]
mod.predict <- predict(mod.fit.nom.density, newdata = new_data, type = "probs")
mod.predict
```

# Part 4
How could we determine a classification for the kernels?
```{r}
predict(mod.fit.nom.density, type="class")
```

# Part 5
What does head(mod.fit$fitted.values) do?
```{r}
head(mod.fit.nom.density$fitted.values)
```

# Part 6
How could you estimate the covariance matrix and print it in R?
```{r}
vcov(mod.fit.nom.density)
```

# Part 7
How could you include some type of transformation of an explanatory variable(s) in the model?
```{r}
mod.fit.nom.density2 <- multinom(formula = type ~ class + density + hardness + size + weight + moisture + weight:size, data = wheat)
summary(mod.fit.nom.density2)
```



